Semantic Frame Induction

### 2014-12-15 Paper/presentation.tex
standardize plate diagrams
add EM and Gibbs steps

@@

\section{Models}
\begin{frame}
  \frametitle{Model 0 - EM }
  \begin{tikzpicture}
    % Nodes
    \node[obs] (datapoint) {$w_v,w_s,w_o$} ; %
    \node[latent, above=of datapoint] (F) {$f$} ; %
    \node[latent, left=of F] (theta) {$\theta$}; %
    \node[latent, right=of datapoint] (phi) {$\varphi_v,\varphi_s,\varphi_o$}; %
    \edge {theta} {F} ; %
    \edge {F} {datapoint}
    \edge {phi} {datapoint} ; %
    \plate {tuples} { (datapoint) } {$N$}; %
    \plate {} { (tuples) (F) (phi)} {$F$} ; %
  \end{tikzpicture}
\begin{tabbing}
  $N$ \hspace{64pt}\= number of data points\\
  $F$\> number of frames\\
  $\theta$\> distribution over frames\\
  $\varphi_a$ \> distribution per argument $a$ (for frame $f$)\\
  $w_v,w_s,w_o$\> datapoint (verb, subject, object)\\
\end{tabbing}
\end{frame}

\section{Results}
\begin{frame}
  \frametitle{Evaluation metrics}
  \begin{itemize}
  \item Frame coherency: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random choses verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$  
  \item Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
  \end{itemize}
\end{frame}

@@

>>>>

\usepackage{natbib}
\bibliographystyle{plain}
\renewcommand\phi\varphi

@@

\section{Models}

\begin{frame}
  \frametitle{Model 0 - EM }
  \begin{columns}
  \column{.5\textwidth}
    \begin{figure}
    \input{model0plate.tex}
    \end{figure}
  \column{.5\textwidth} 
  \begin{scriptsize}
  \begin{tabbing}
    $N$ \hspace{10pt}\= number of data points\\
    $F$              \> number of frames\\
    $\theta$         \> distribution over frames\\
    $\varphi_a$      \> distributions (for each frame) over \\ 
                     \> vocabulary of argument $a$\\
    $w_a$            \> datapoint (verb, subject, object)\\
  \end{tabbing}
  \end{scriptsize}
  \end{columns}
\footnotesize{E-Step:}
\[
P(f|w_i) = \frac{\prod_a^{\{v,s,o\}}P(w_i^a|\phi_f^a) P(f|\theta)}{\sum_{f'}^F\prod_a^{\{v,s,o\}}P(w_i^a|\phi_{f'}^a)}
\]
\footnotesize{M-Step:}
\begin{columns}
\column{.5\textwidth}
\[
P(f|\theta) = \frac{\sum_{i=1}^N \mu_i(f)}{\sum_{f'=1}^F\sum_{i=1}^N\mu_i(f')}
\]
\column{.5\textwidth}
\[
P(w|\phi_f^a) = \frac{\sum_{i=1}^N \mu_i(f) C(w,a)}{\sum_{w'=1}^{V^a}\sum_{i=1}^N \mu_i(f) C(w',a)}
\]
\end{columns}
\end{frame}

\begin{frame}
  \begin{columns}
  \column{.5\textwidth}
  \frametitle{Model 1 - Gibbs Sampling}
  \begin{figure}
  \input{model1plate.tex}
  \end{figure}
  \column{.5\textwidth}
  \begin{scriptsize}
  \begin{tabbing}
    $N$ \hspace{10pt}\= number of data points\\
    $F$              \> number of frames\\
    $V$              \> number of documents (= verb vocabulary)\\
    $\theta$         \> distribution over frames\\
    $\varphi_a$      \> distributions (for each frame) over \\ 
                     \> vocabulary of argument $a$\\
    $w_a$            \> datapoint (verb, subject, object)\\
    $\beta$          \> hyperprior for $\varphi$ (for each argument)\\
    $\alpha$         \> hyperprior for $\theta$ \\
  \end{tabbing}
  \end{scriptsize}
  \end{columns}
\footnotesize{Gibbs:}
\[
P(z_{ij} = f| \mathbf{f}_{-ij},\alpha,\beta,w)
\propto \prod_a^{\{v,s,o\}}\frac{\beta^a + \tilde{C}(f,w_{ij})}{V^a + \tilde{C}(f)}
        \cdot \frac{\alpha + \tilde{C}(i,f)}{F\alpha+\tilde{C}(i)}
\]
\begin{scriptsize}
  \begin{tabbing}
    $\tilde{C}(f,w_{ij})$ \hspace{10pt}\= count times $w_{ij}$ is assigned to frame $f$\\
    $\tilde{C}(f)$                     \> count total data points assigend to $f$\\
    $\tilde{C}(i,f)$                   \> count sentences in document $i$ assigned to $f$\\
    $\tilde{C}(i)$                     \> count sentences in document $i$\\ 
  \end{tabbing}
  \end{scriptsize}

\end{frame}

\section{Results}

\begin{frame}
  \frametitle{Evaluation metrics}
  \begin{itemize}
  \item Frame coherency: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random choses verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$  
  \item Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
  \end{itemize}
\end{frame}

@@

\section{References}
\begin{frame}[t,allowframebreaks]
\nocite{*}
\bibliography{refs.bib}
\end{frame}
